Supplementary Materials

### 2023-07-21 manuscript/supplementary.tex
ms updates

  \caption{The standard (dark gray) and rescaled (blue) B' maps for different
  $\mu = 1.6 \times 10^{-8}$ and three different selection coefficients. For
$s=10^{-5}$ ($2N_e s = 0.2$), locally-rescaling alters the predicted reduction
so that it is essentially insignificant ($B \approx 1$). }

>>>>

  \caption{The standard (dark gray) and rescaled (blue) B' maps for different
      $\mu = 1.6 \times 10^{-8}$ and three different selection coefficients.
      For $s=10^{-5}$ ($2N_e s = 0.2$), locally-rescaling alters the predicted
      reduction so that it is essentially insignificant ($B \approx 1$). For
  mid-strength selection $s=10^{-4}$ ($2N_e s = 2$), there is only a very
slight difference between standard and locally-rescaled B' maps. Finally, for
strong selection $s=10^{-3}$ ($2N_e s = 20$), locally-rescaling does not change
the B' maps, as expected. }
\end{figure}

\begin{figure}[htbp]
    \label{suppfig:rescale-dfe}
  \centering
  \includegraphics[]{figures/supplementary/rescale_DFE.pdf}

  \caption{The DFE for YRI samples with locally-rescaling. The maximum
  likelihood mutation rate estimate for this is $\widehat{\mu} = 8 \times
10^{-8}$, which is the upper boundary of the range used during optimization.}
